NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-31 results.tex
minor mod
add description of both results w/ and w/o jet-veto in absolute plot

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon 
    in triple photon production at the LHC at 13\,TeV. 
    The distributions are shown at LO (blue), NLO QCD (green), 
    NLO EW (orange), NLO \QCDpEW\ (black) and NLO \QCDtEW\ (red) 
    including scale uncertainties. The top ratio plot details 
    the relative corrections to the leading order cross section 
    without applying any jet veto, while the centre ratio plot 
    applies a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$. 
    The lower ratio highlights the size of the electroweak corrections.
    \label{fig:aaa:pt}
  }
\end{figure}

@@

Finally, Figure \ref{fig:aaw:dphi} presents the azimuthal 
separations of the leading and the subleading photon, and 
both the leading and subleading photon and the lepton. 
Contrary to \aaa\ production, no kinematic constraints 
are present at LO, owing to the difference in flavour 
between the considered objects and the fact that the 
lepton is only one of two decay products of the $W$ which 
takes the role of the third photon from point of view of 
the contributing diagrams.

Both the QCD and EW corrections are generally flat, taking 
values of typically $\deltaQCD=1-2$ in absence and 
$\deltaQCD=0.4$ in presence of a jet veto, and 
$\deltaEW=-2\%$.

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaa/pT_y3}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon 
    in triple photon production at the LHC at 13\,TeV. 
    The distributions are shown at LO (blue), NLO QCD (green), 
    NLO EW (orange), NLO \QCDpEW\ (black) and NLO \QCDtEW\ (red) 
    including scale uncertainties. The top panel displays the 
    absolute predictions for both the case with and without the 
    application of a jet veto of $p_\mathrm{T,jet}^\mathrm{veto}=\text{30\,GeV}$, 
    the latter ones are easily recognisable 
    due to their much reduced rate. The top ratio plot details 
    the relative corrections to the leading order cross section 
    without applying the jet veto, while the centre ratio plot 
    applies the jet veto. 
    The lower ratio highlights the size of the electroweak corrections.
    \label{fig:aaa:pt}
  }
\end{figure}

@@

Finally, Figure \ref{fig:aaw:dphi} presents the azimuthal 
separations of the leading and the subleading photon, and 
both the leading and subleading photon and the lepton. 
Contrary to \aaa\ production, no kinematic constraints 
are present at LO, owing to the difference in flavour 
between the considered objects and the fact that the 
lepton is only one of two decay products of the $W$ which 
takes the role of the third photon from point of view of 
the contributing diagrams. 
Both the QCD and EW corrections are generally flat, taking 
values of typically $\deltaQCD=1-2$ in absence and 
$\deltaQCD=0.4$ in presence of a jet veto, and 
$\deltaEW=-2\%$.
